Gaussian Process regression for astronomical time-series

### 2022-08-12 src/tex/ms.tex
[showyourwork] overleaf sync
[showyourwork] nothing

\begin{figure}[ht]
  \centering
  \script{quasar.ipynb}
  \begin{minipage}[t]{0.48\linewidth}
    \includegraphics[width=\linewidth,vshift=1cm]{figures/quasar.pdf} 
  \end{minipage} \hfill
  \begin{minipage}[t]{0.48\linewidth}
    \includegraphics[width=\linewidth,vshift=1cm]{figures/quasar_posteriors.pdf}
  \end{minipage}
  \caption{Simulated datasets for the lensed quasar and transit examples. In the left panel, black dots and crosses with error bars show the light curves of the two quasar images, respectively, while the thin blue and red lines show the corresponding posterior samples for the simultaneous fit to both light curves using a Mat{\'e}rn $3/2$ GP.  In the right panel, black dots with error bars show the transit observations, while the thin blue and red lines lines show posterior samples for the models with white noise only and with a squared exponential GP, respectively. The posterior distributions for the models fit to both datasets are shown in Figure~\protect\ref{fig:sim_posteriors}. The {\sc Jupyter} notebooks used to produce this figure are available as Supplementary Material (\texttt{quasar\_time\_delay.ipynb} and \texttt{transit\_modelling.ipynb}).}
  \label{fig:sim_lcs}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \begin{minipage}[t]{0.48\linewidth}
    \includegraphics[align=c,width=\linewidth,vshift=1cm]{figures/transit.pdf} 
  \end{minipage} \hfill
  \begin{minipage}[t]{0.48\linewidth}
    \includegraphics[align=c,width=\linewidth,vshift=1cm]{figures/transit_posteriors.pdf}
  \end{minipage}
  \caption{Corner plots for the fits to the two simulated quasar and transit light curves (left and right, respectively) shown in Figure~\ref{fig:sim_lcs}.  
  In each panel, the plots along the diagonal show 1-D histograms of the posterior samples for a subset of the fitted parameters, with vertical dashed lines indicating the 16$^{\rm th}$ and 84$^{\rm th}$ percentiles, while the off-diagonal plots show 2-D correlations between pairs of parameters. The horizontal and vertical solid black lines in each panel show the ``ground truth''. In the quasar case, we show the distribution for the GP variance $A$ and length scale $\lambda$ \suz{ensure notation consistent}, as well as for the time delay $\delta t$. In the transit case, the results of the white-noise only fit are shown in blue, while those of the GP fit are shown in red. These plots were generated using the {\sc corner.py} package \citep{corner}. \dan{How can we have them overlap with the transit one in the top right and the quasar one in the bottom left?} The {\sc Jupyter} notebooks used to produce this figure are available as Supplementary Material (\texttt{quasar\_time\_delay.ipynb} and \texttt{transit\_modelling.ipynb}).}
  \label{fig:sim_posteriors}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
  \script{quasar.ipynb}
  \begin{minipage}[t]{0.5\linewidth}
    \includegraphics[width=\linewidth,vshift=1cm]{figures/quasar.pdf}
  \end{minipage} \hfill
  \begin{minipage}[t]{0.44\linewidth}
    \includegraphics[width=\linewidth]{figures/quasar_posteriors.pdf}
  \end{minipage}
  \caption{Simulated datasets for the lensed quasar and transit examples. In the left panel, black dots and crosses with error bars show the light curves of the two quasar images, respectively, while the thin blue and red lines show the corresponding posterior samples for the simultaneous fit to both light curves using a Mat{\'e}rn $3/2$ GP.  In the right panel, black dots with error bars show the transit observations, while the thin blue and red lines lines show posterior samples for the models with white noise only and with a squared exponential GP, respectively. The posterior distributions for the models fit to both datasets are shown in Figure~\protect\ref{fig:sim_posteriors}. The {\sc Jupyter} notebooks used to produce this figure are available as Supplementary Material (\texttt{quasar\_time\_delay.ipynb} and \texttt{transit\_modelling.ipynb}).}
  \label{fig:sim_lcs}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \script{transit.ipynb}
  \begin{minipage}[t]{0.5\linewidth}
    \includegraphics[width=\linewidth,vshift=1cm]{figures/transit.pdf}
  \end{minipage} \hfill
  \begin{minipage}[t]{0.44\linewidth}
    \includegraphics[width=\linewidth]{figures/transit_posteriors.pdf}
  \end{minipage}
  \caption{Corner plots for the fits to the two simulated quasar and transit light curves (left and right, respectively) shown in Figure~\ref{fig:sim_lcs}.
  In each panel, the plots along the diagonal show 1-D histograms of the posterior samples for a subset of the fitted parameters, with vertical dashed lines indicating the 16$^{\rm th}$ and 84$^{\rm th}$ percentiles, while the off-diagonal plots show 2-D correlations between pairs of parameters. The horizontal and vertical solid black lines in each panel show the ``ground truth''. In the quasar case, we show the distribution for the GP variance $A$ and length scale $\lambda$ \suz{ensure notation consistent}, as well as for the time delay $\delta t$. In the transit case, the results of the white-noise only fit are shown in blue, while those of the GP fit are shown in red. These plots were generated using the {\sc corner.py} package \citep{corner}. \dan{How can we have them overlap with the transit one in the top right and the quasar one in the bottom left?} The {\sc Jupyter} notebooks used to produce this figure are available as Supplementary Material (\texttt{quasar\_time\_delay.ipynb} and \texttt{transit\_modelling.ipynb}).}
  \label{fig:sim_posteriors}
\end{figure}
